### 2013-07-29 doc/asplos14/evaluation.tex

We look at two classes of trees, T1 and T3, from
the original benchmark. T1 trees are very shallow and wide (i.e., significant
parallel slack \cite{Valiant:1990}), while T3 trees are very deep (i.e., little parallel slack).
Given that access to each vertex is a random access, the critical path to search
T3 trees is very long, hence the low performance and scalability. On such
trees, we do not expect there to be sufficient concurrency for any system,
including \Grappa, to achieve high throughput -- at the 16-node data point,
the average active tasks per core over the search is 775 for T1 and
only 13 for T3. Given the lack of parallelism, scaling up only serves
to reduce throughput by distributing the tree to more machines.
On the other hand, \Grappa performs and scales very well for T1
trees.

>>>>

We look at two classes of trees, T1 and T3, from
the original benchmark. T1 trees are very shallow and wide (i.e., significant
parallel slack \cite{Valiant:1990}), while T3 trees are very deep (i.e., little parallel slack).
Given that access to each vertex is a random access, the critical path to search
T3 trees is very long, hence the low performance and scalability. On such
trees, we do not expect there to be sufficient concurrency for any system,
including \Grappa, to achieve high throughput -- at the 16-node data point,
the average active tasks per core over the search is an order of magnitude larger for T1 than for T3.
 Given the lack of parallelism, scaling up only serves
to reduce throughput by distributing the tree to more machines.
On the other hand, \Grappa performs and scales very well for T1
trees.
